---
title: "p8105_hw6_sz2800"
author: "Stephanie Zhen"
date: "11/25/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(modelr)
library(purrr)
```

## Q1: Baby's birthweight

Cleaning data.
```{r}
hw6_bw = read.csv("./data/birthweight.csv")

bw_clean = hw6_bw %>% 
  janitor::clean_names() %>% 
  mutate(babysex = ifelse(babysex == 1, "male", "female"),
        babysex = as.factor(babysex)) %>% 
  mutate(frace = as.factor(frace),
         frace = recode_factor(frace, '1' = "white", '2' = "black", '3' = "asian", '4' = "puerto rican", '8' = "other", '9' = "unknown")) %>% 
  mutate(malform = ifelse(malform == 0, "absent", "present"),
         malform = as.factor(malform)) %>% 
  mutate(mrace = as.factor(mrace),
         mrace = recode_factor(mrace, '1' = "white", '2' = "black", '3' = "asian", '4' = "puerto rican", '8' = "other"))


summary(bw_clean)
```

Recoded the baby's sex, father's race, mother's race, and malform into factor variables and appropriate labels. There doesn't seem to have any NA's in this dataset. 

Model building for outcome birthweights
```{r}
bw_fit = lm(bwt ~ babysex + ppbmi + gaweeks + smoken + blength, data = bw_clean) 
bw_fit %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value)

bw_fit
```

Inital online research shows that mother's BMI, gender of baby, length of pregnancy, and mother's lifestyle, length of baby are known factors that can influence the birthweight of the baby. Therefore, for the model buliding, I use the variables, babysex, ppbmi, gaweeks, smoken, blength as predictors for the outcome, birthweight, bwt. Since birthweight is a continuous outcome, I will use linear regression. 


Prediction and residual plot
```{r}
bw_resid = bw_clean %>% 
  modelr::add_residuals(bw_fit)

bw_pred = bw_clean %>% 
  modelr::add_predictions(bw_fit) %>% 
  select(pred)

bw_resid_pred = cbind(bw_resid, bw_pred)

bw_pred_resid_plot = ggplot(bw_resid_pred, aes(x = pred, y = resid)) +
  geom_point()

bw_pred_resid_plot
```


Model 2: using length at birth and gestational age as predictors (main effects only):
```{r}
bw_meffect = lm(bwt ~ gaweeks + blength, data = bw_clean) 
bw_meffect %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value)

bw_meffect
```


Model 3: using head circumference, length, sex, and all interactions (including the three-way interaction).
```{r}
bw_interact = lm(bwt ~ bhead + blength + babysex + (bhead * blength) + (bhead * babysex) + (blength * babysex) + (bhead * blength * babysex), data = bw_clean) 
bw_interact %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value)

bw_interact
```

In order to correctly define a three way interaction, I must also include all the two way interaction terms and main effects as well. 


Comparing my model with the model with just the main effects and model with the three way interaction. 
```{r}
bw_cv = 
  crossv_mc(bw_clean, 100) 

bw_cv =
  bw_cv %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

bw_cv = bw_cv %>% 
  mutate(
    bw_fit = map(train, ~lm(bwt ~ babysex + ppbmi + gaweeks + smoken + blength, data = .x)),
    bw_meffect = map(train, ~lm(bwt ~ gaweeks + blength, data = .x)),
    bw_interact = map(train, ~lm(bwt ~ bhead + blength + babysex + (bhead * blength) + (bhead * babysex) + (blength * babysex) + (bhead * blength * babysex), data = .x))) %>% 
  mutate(
    rmse_bw_fit = map2_dbl(bw_fit, test, ~rmse(model = .x, data = .y)),
    rmse_meffect = map2_dbl(bw_meffect, test, ~rmse(model = .x, data = .y)),
    rmse_interact = map2_dbl(bw_interact, test, ~rmse(model = .x, data = .y))
  )
```

Prepping for graphing root mean square error and plotting it
```{r}
bw_cv_pre = bw_cv %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_")



bw_cv_plot = 
  ggplot(bw_cv_pre, aes(x = model, y = rmse)) + 
  geom_violin()


bw_cv_plot
```

The model with the 3 way interaction term has the lowest root mean square error and thus seems to be the model that predicts birthweight best. However, it is also the model with the most variables and is not parsimonious. My model has 5 variables and has similar root mean square error with the model that has only the main effect (2 variables). Therefore, the most parsimonious model is the model with only the main effects, and the model with the lowest root mean square error is the model with the three way interaction. 


## Question 2:
```{r}
set.seed(1)

weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

```


Linear model with tmin as predictor and tmax as response
```{r}
weather_mod = lm(tmax ~ tmin, data = weather_df) %>% 
  broom::glance()

boot_sample = function(df) {
  sample_frac(df, replace = TRUE)
}

```


Wrangling data to plot log(beta0 * beta1) estimates
```{r}
log_beta_pre = weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  select(-std.error, -statistic, -p.value) %>% 
  pivot_wider(
    names_from = term,
    values_from = estimate)

names = c("id", "beta0", "tmin")
colnames(log_beta_pre) = names

log_beta = log_beta_pre %>% 
  mutate(log_bvalue = log(beta0 * tmin))

log_beta_plot = log_beta %>% 
  ggplot(aes(x = log_bvalue)) +
  geom_density()

log_beta_plot
```


```{r}
r2_pre = weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results)

r2_plot = r2_pre %>% 
  ggplot(aes(x = r.squared)) +
  geom_density()

r2_plot
```

